\documentclass[12pt]{article}

\newcommand{\ignore}[1]{}

\usepackage[margin=1in]{geometry}
\usepackage{url,hyperref}
\usepackage{tabularx}
\usepackage{bold-extra}
\usepackage{xcolor}
%\usepackage[T1]{fontenc}

\begin{document}

%\vspace{-0.5in}
\noindent\rule{\textwidth}{1pt}
\begin{center}
\LARGE
\vspace{-0.15in}
Mike Izbicki
\end{center}
\vspace{-0.15in}
\noindent\rule{\textwidth}{1pt}
\vspace{0.05in}

%\vspace{0.15in}
\noindent
{{\scshape \bfseries {About Me}}}
\vspace{0.05in}

\noindent
\begin{tabularx}{\textwidth}{X}
I am a phd student at UC Riverside.
I study how to make machine learning algorithms faster under Dr.\ Christian Shelton.
Most of my projects are listed on github (\url{http://github.com/mikeizbicki}) and my personal webpage (\url{http://izbicki.me}).
The best way to contact me is via email at \url{mike@izbicki.me}.
\end{tabularx}

%\noindent
%\begin{tabular}{ll}
%email & \url{mike@izbicki.me} \\
%personal website & \url{http://izbicki.me} \\
%github page & \url{http://github.com/mikeizbicki} \\
%\end{tabular}

\vspace{0.15in}
\noindent
{{\scshape \bfseries {Education}}}
\vspace{0.05in}


\noindent
\begin{tabularx}{\textwidth}{Xr}
\textbf{University of California Riverside} & 2011-Present \\
PhD, Computer Science \vspace{0.05in}& \\
%\textbf{Naval Nuclear Propulsion Training Command} & 2009 \\
%Engineering officer of the watch on S5W submarine nuclear reactor \vspace{0.05in}& \\

%\textbf{Johns Hopkins University Applied Physics Laboratory} & 2008 \\
\textbf{Johns Hopkins University} & 2008 \\
MS, Computer Science \vspace{0.05in}& \\

\textbf{United States Naval Academy} & 2004-2008 \\
BS, Computer Science \vspace{0.05in}& \\

\end{tabularx}

%I received the following academic awards:
%\begin{enumerate}
%\item UCR dean's fellowship recipient partially funding my phd
%\item VGEP scholarship recipient funding my masters degree
%\end{enumerate}

\vspace{0.15in}
\noindent
{{\scshape \bfseries {Teaching}}}
\vspace{0.05in}

%I taught the following courses at the [Pyongyang University of Science and Technology](https://pust.co):

\noindent
I was the lecturer at the Pyongyang University of Science and Technology (PUST) for:

\noindent
\begin{tabularx}{\textwidth}{Xr}
Modern Software & Fall 2016 \\
%Algorithm Design & Fall 2016, Fall 2015 \\
Algorithm Design & Fall 2016 \\
Algorithm Design & Fall 2015 \\
Discrete Math & Fall 2015
\end{tabularx}

\vspace{0.1in}
\noindent
I was the lecture at the University of California Riverside (UCR) for:

\noindent
\begin{tabularx}{\textwidth}{Xr}
%Software Construction & Spring 2015, Winter 2015,                        \\
                      %&                           Fall 2014, Summer 2014 \\
Software Construction & Spring 2015 \\
Software Construction & Winter 2015                        \\
Software Construction & Fall 2014 \\
Software Construction & Summer 2014 \\
Introduction to the World Wide Web & Winter 2014 \\
Intermediate Data Structures and Algorithms & Fall 2013 \\
Introduction to Data Structures & Spring 2013 \\
\end{tabularx}

\vspace{0.1in}
\noindent
I was a teaching assistant at UCR for:

\noindent
\begin{tabularx}{\textwidth}{Xr}
Software Construction & Spring 2014 \\
Introduction to Computer Science II & Winter 2013 \\
Introduction to Computer Science I  & Fall 2012 \\
Computer Security & Fall 2012 \\
\end{tabularx}

%\vspace{0.15in}
\newpage
\noindent
{{\scshape \bfseries {Research}}}
\vspace{0.05in}

\noindent
Papers currently under review:
\begin{enumerate}
\item
Mike Izbicki, and Christian Shelton.
``Communication-Efficient Distributed Maximum Likelihood Estimation with the Optimal Weighted Average.''

\end{enumerate}

\noindent
Refereed papers:

\begin{enumerate}
\item
Mike Izbicki, Sajjad Amini, Christian Shelton, and Hamed Mohensian-Rad.
``Identification of Destabilizing Attacks in Power Systems''
American Controls Conference (ACC),
2017.

\item
Mike Izbicki, Christian Shelton.
``Faster Cover Trees,''
International Conference of Machine Learning (ICML),
2015.

\item
Mike Izbicki.
``Algebraic classifiers: a generic approach to fast cross-validation, online training, and parallel training,''
International Conference of Machine Learning (ICML),
2013.
\end{enumerate}

\noindent
Workshop papers, invited presentations, and small articles:

\begin{enumerate}
\item
``Faster Cover Trees'' presented at CalState Fullerton, August 2016.

\item
``Open Sourcing the Classroom.''  Graduate student research competition at SigCSE 2016.  {\textcolor{red}{3rd place award}}.

\item
``Open Sourcing the Classroom.''  International Conference of the Pyongyang University of Science and Technology (IcoPUST), 2015.

\item
``Bashing Haskell: Reimplementing Haskell's Parsec Library in the Unix Shell.''
SigBOVIK 2015.

\item
``Modeling data with algebra.'' Workshop on Data Centric Programming (DCP), 2014.

\item
``HLearn: a machine learning library for Haskell.''
Trends in Functional Programming (TFP), 2013.

\item
``The open source software package HLearn.''
Workshop on Machine Learning Open Source Software (MLOSS), 2013.

\item
``Two monoids for solving NP-complete problems.''
The Monad Reader, 2013.

\item
``Machine learning? Why not monoids?''
Presented at Facebook, September 2013.
\end{enumerate}

%\noindent
%Articles on nuclear policy:
%
%\begin{enumerate}
%\item
%Book review: ``The steps to war,'' International Journal on World Peace, December 2011.
%
%\item
%Book review: ``Elements of a nuclear disarmament treaty,'' Defense Threat Reduction University Journal 2, 2010.
%
%\item
%``What's wrong with America's nuclear hawks?,'' Strategic Studies Quarterly, Winter 2010.
%\end{enumerate}

\end{document}

### Research

Conference papers:

* [Faster Cover Trees](http://izbicki.me/public/papers/icml2015-faster-cover-trees.pdf), with Christian Shelton.  International Conference of Machine Learning (ICML) 2015.

* [Algebraic classifiers: a generic approach to fast cross-validation, online training, and parallel training](https://izbicki.me/public/papers/icml2013-algebraic-classifiers.pdf).  International Conference of Machine Learning (ICML) 2013.

<!--Don Needham and Michael Izbicki, "High energy laser progressive wavefront modeling," Proceedings of the International Conference on Software Engineering Research and Practice (SERP'07), Las Vegas, NV, 25-28 June 2007. pp. 137-143.-->

Workshops / invited presentations / small articles:

* "Faster Cover Trees" presented at CalState Fullerton, August 2016.

* Open Sourcing the Classroom.  Graduate student research competition at SigCSE 2016.  <font color=red>3rd place award</font>.

* [Open Sourcing the Classroom](http://izbicki.me/public/papers/icopust2015.pdfa).  International Conference of the Pyongyang University of Science and Technology (IcoPUST) 2015.

* [Bashing Haskell: Reimplementing Haskell's Parsec Library in the Unix Shell](https://github.com/mikeizbicki/parsed/raw/master/sigbovik2015/paper.pdf). SigBOVIK 2015.

* "Modeling data with algebra," Workshop on Data Centric Programming (DCP) 2014.

* [HLearn: a machine learning library for Haskell,](https://izbicki.me/public/papers/tfp2013-hlearn-a-machine-learning-library-for-haskell.pdf) Trends in Functional Programming (TFP) 2013.

* The open source software package HLearn. Workshop on Machine Learning Open Source Software (MLOSS) 2013.

* [Two monoids for solving NP-complete problems](https://izbicki.me/public/papers/monoids-for-approximating-np-complete-problems.pdf). The Monad Reader, 2013.

* "Machine learning? Why not monoids?" presented at Facebook, September 2013.

<!--* Don Needham and Michael Izbicki, "USNA high energy laser educational initiative," High Energy Laser Joint Technology Office (HEL-JTO) Annual Review, Albuquerque, NM, 01-04 May 2007.-->

<!--Online presence

* [My github page](http://github.com/mikeizbicki/) contains a number of open source contributions

* My personal blog ([izbicki.me](http://izbicki.me)) contains technical discussions related to my research
-->

<!--
Non-computer science writing:

* "The steps to war," International Journal on World Peace, December 2011.

* "The human faces of god," Anglican Theological Review, Spring 2011.

* "What's wrong with America's nuclear hawks?," Strategic Studies Quarterly, Winter 2010.

* "Elements of a nuclear disarmament treaty," Defense Threat Reduction University Journal 2, 2010.
-->

<!--
### Military experience

I was in the navy from 2004-2011.
Most of this time was spent in training at either the Naval Academy or NNPTC.
I left the navy as a conscientious objector.
The NYTimes did a [rather nice writeup](http://www.nytimes.com/2011/02/23/nyregion/23objector.html?pagewanted=all&_r=0) of my discharge,
and I have [a number of blog posts](https://izbicki.me/#my%20conscientious%20objector%20discharge) about the topic.
This experience is a hugely important part of my life.
I enjoy sharing it with others, and have given a number of small presentations about it.
If you have any questions, please ask!
-->
}
