\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{url}
\usepackage{tabularx}
\usepackage{xcolor}

\newcommand{\school}[2]{\textcolor{red}{\textbf{{#1}:} {#2}}}

\begin{document}

\noindent
\hspace{-0.13in}
\begin{tabularx}{1.03\textwidth}{Xr}
 & Mike Izbicki \\
 & 206 Knox Ct\\
 & Riverside, CA 92507\\
 & mike@izbicki.me\\
\end{tabularx}

\vspace{0.2in}

\setlength{\parskip}{15pt plus4mm minus3mm}
\pagenumbering{gobble}

\noindent
Dear faculty search committee:

\noindent
I am applying for the assistant professor position,
which I found via your webpage.
I'm currently a postdoc at UC Riverside's Data Science Center,
where my research applies machine learning theory to big social media data.
I have experience teaching diverse student populations both in the United States and Korea,
%Prior to that I held teaching appointments in both the United States and Korea, 
%where I taught both undergraduate and graduate students.
and I also have industry experience from 7 years in the US Navy working on cyber-security and nuclear reactors.
I believe this experience makes me a great fit for your department.

\noindent
%My research sits at the intersection of statistics, computation, and social justice.
My research develops machine learning algorithms that have a positive social impact.
%and so I would be particularly excited to work at an institution like LMU that values social justice.
%My research is particularly well suited for a liberal arts college like CMC because I develop machine learning algorithms that will have a positive social impact.
%My research develops machine learning algorithms with strong theoretical guarantees suitable for large scale social media data.
%In particular, social media platforms are generating more data everyday from around the world,
%and I study new large scale learning algorithms designed to better understand this data.
For example, most research analyzing social media messages has focused on only English language messages,
and so we have little understanding of how minority language communities interact online.
To address this issue, I've developed techniques for analyzing the more than 100 non-English languages used everyday on Twitter.
I've also developed techniques to prevent malicious users from corrupting machine learning algorithms with racist messages or fake news.
%Most of the algorithms I've developed have associated theorems that guarantee their real world performance.
%These algorithms have associated theorems that guarantee their real world performance.
I'm excited to help students work on similar high impact problems.
%I strive to provide rigorous, provable guarantees for the algorithms I develop.
%All of my research projects apply mathematical theories to computational social challenges.

\noindent
I enjoy teaching,
and I'm able to teach a broad range of courses.
I've previously taught 11 university courses,
which ranged from introductory courses for humanities majors to advanced graduate-level machine learning courses.
Students like my teaching and have consistently rated my ``effectiveness as a teacher overall'' in at least the 80th percentile.
I'm particularly interested in teaching courses on computational statistics, numerical optimization, and machine learning,
%but I'm also able to teach any course in the undergraduate math or computer science curricula.
but I am also able to teach all courses in the undergraduate curriculum.
I have experience working with students from many cultures in the US and Korea,
and I'm committed to making my classrooms an inclusive environment where all students can succeed.

\noindent
One of my goals as a professor would be to help students contribute to open source software.
Modern data science increasingly depends on open source projects like R, SciPy, and Octave,
and I hope to help students contribute to the next generation of these tools.
%I have already designed and taught award-winning courses to teach open source,
%and the resulting curricula earned an award from SIGCSE's graduate student research competition.
%Through these courses and other mentoring, 
%and through these courses I've helped students contribute to open source projects with collaborators from around the world.
I designed some of the first courses to teach students how to contribute to open source software,
and the resulting curricula earned an award from SIGCSE's graduate student research competition.
Through these courses and other mentoring, 
I've helped students contribute to and start their own open source projects with collaborators from around the world.
I specifically hope to offer a course on open source data science 
and to integrate open source more closely with the students' other courses.

\noindent
Thank you for your consideration.
If you have any questions,
please do not hesitate to ask.

\noindent
Regards,

\vspace{-0.10in}
\noindent
Mike Izbicki

%\school{?}{ Christopher T. Ryu: machine learning; Paul Salvador Inventado: data mining for education; }
%
%\school{cpp}{Hao Ji: machine learning and hpc; Amar Raheja: image analysis; Daisy Tang: machine learning for robots; Lan Yang: big data; }
%
%\school{csusb}{Haiyan Qiao: machine learning applied to bioinformatics and games; George M. Georgiou: neural networks with complex numbers;  Qingquan Sun: Compressive Sensing and Machine Learning; Yan Zhang: data mining, distributed computing; }
%
%\school{HMC}{Ben Wiedermann: programming languages; Christopher A. Stone: type theory; George D. Montañez: why machine learning works (hired in 2017); Julie Medero: NLP}
%
%\school{CMC}{Dr. Jeho Park is a co-founder and the Director of Data Analysis for SoDAVi (Social Data Analysis and Visualization), a non-profit organization. He was also elected President (2019 term) of the Korean-American Computer Scientists and Engineers Association. His research and career interests are in high performance computing, data science, AI/Machine Learning, and computer science and mathematics education.}
%
%\school{SDSU}{Dr. Tao Xie, Dr. Mary Thomas: high performance and parallel computing; Dr. Marko Vuskovic: machine learning for robots; Dr. Faramarz Valafar: machine learning for bioinformatics; Dr. Marie Roch: machine learning for mapping marine biology}


\end{document}
