\documentclass[12pt]{article}

\newcommand{\ignore}[1]{}

\usepackage[margin=1in]{geometry}
\usepackage{url,hyperref}
\usepackage{tabularx}
\usepackage{bold-extra}
\usepackage{xcolor}
%\usepackage[T1]{fontenc}
\usepackage{hyperref}
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor    = blue  %Colour of citations
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\section*{Publication List for Mike Izbicki}

\noindent
Currently under review:
\begin{enumerate}
\item
Mike Izbicki, Vagelis Papalexakis, Vassilis Tsotras.
``Geolocating Tweets Written in Any Language Sent from Any Location.''

\item
Mike Izbicki.
``Gradient Clipping Makes Stochastic Gradient Descent Robust to Adversarial Noise.''

\item
Mike Izbicki, and Christian Shelton.
``Communication-Efficient Distributed Maximum Likelihood Estimation with the Optimal Weighted Average.''

\end{enumerate}

\noindent
Refereed papers:

\begin{enumerate}
\setcounter{enumi}{3}
\item
Mike Izbicki, Sajjad Amini, Christian Shelton, and Hamed Mohensian-Rad.
``Identification of Destabilizing Attacks in Power Systems''
American Controls Conference (ACC),
2017.

\item
Mike Izbicki, Christian Shelton.
``Faster Cover Trees,''
International Conference of Machine Learning (ICML),
2015.

\item
Mike Izbicki.
``Algebraic classifiers: a generic approach to fast cross-validation, online training, and parallel training,''
International Conference of Machine Learning (ICML),
2013.
\end{enumerate}

%\newpage
\noindent
Workshop papers, invited presentations, and small articles:

\begin{enumerate}
\setcounter{enumi}{6}
\item
``Merging Neural Networks.''  Presented at SoCalML, August 2017.

\item
``Faster Cover Trees.''  Presented at CalState Fullerton, August 2016.

\item
``Open Sourcing the Classroom.''  Graduate student research competition at SigCSE 2016.  Received 3rd place award.

\item
``Open Sourcing the Classroom.''  International Conference of the Pyongyang University of Science and Technology (IcoPUST), 2015.

\item
``Bashing Haskell: Reimplementing Haskell's Parsec Library in the Unix Shell.''
SigBOVIK 2015.

\item
``Modeling data with algebra.'' Workshop on Data Centric Programming (DCP), 2014.

\item
``HLearn: a machine learning library for Haskell.''
Trends in Functional Programming (TFP), 2013.

\item
``The open source software package HLearn.''
Workshop on Machine Learning Open Source Software (MLOSS), 2013.

\item
``Two monoids for solving NP-complete problems.''
The Monad Reader, 2013.

\item
``Machine learning? Why not monoids?''
Presented at Facebook, September 2013.
\end{enumerate}

%\noindent
%Articles on nuclear policy:
%
%\begin{enumerate}
%\item
%Book review: ``The steps to war,'' International Journal on World Peace, December 2011.
%
%\item
%Book review: ``Elements of a nuclear disarmament treaty,'' Defense Threat Reduction University Journal 2, 2010.
%
%\item
%``What's wrong with America's nuclear hawks?,'' Strategic Studies Quarterly, Winter 2010.
%\end{enumerate}


\end{document}

