\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{url}
\usepackage{tabularx}
\usepackage{xcolor}

\newcommand{\school}[2]{\textcolor{red}{\textbf{{#1}:} {#2}}}

\begin{document}

\noindent
\hspace{-0.13in}
\begin{tabularx}{1.03\textwidth}{Xr}
 & Mike Izbicki \\
 & 206 Knox Ct\\
 & Riverside, CA 92507\\
 & mike@izbicki.me\\
\end{tabularx}

\vspace{0.2in}

\setlength{\parskip}{15pt plus4mm minus3mm}
\pagenumbering{gobble}

\noindent
Dear faculty search committee:

\noindent
I am applying for the Assistant Professor of Computer Science position advertised on your website.
The focus of my research is machine learning,
but I've also done work in programming language design and computer science education research in support of my machine learning work.
I'm currently a postdoc at UC Riverside's Data Science Center,
and prior to that I held teaching appointments in both the United States and Korea, where I taught both undergraduate and graduate students.
I also have industry experience from 7 years in the US Navy working on cyber-security and nuclear reactors.
I believe this experience makes me a great fit for your department.

\noindent
My research makes large scale machine learning easier to use.
In the distributed setting, I focus on algorithms that are easy to implement but still have strong theoretical guarantees.
For example, I developed the first MapReduce algorithm for convex machine learning algorithms with statistically optimal generalization performance.
I also have a number of Haskell libraries that develop new programming language features specifically designed for machine learning.
For example, the \texttt{HerbiePlugin} automatically converts source code into numerically stable forms,
so programmers don't have to worry about the intricacies of floating point arithmetic.

\noindent
I enjoy teaching,
and I'm able to teach a broad range of courses at both graduate and undergraduate levels.
I've previously taught 11 university courses,
which ranged from introductory courses for humanities majors to advanced graduate-level machine learning courses.
Students like my teaching and have consistently rated my ``effectiveness as a teacher overall'' in at least the 80th percentile.
I'm particularly interested in teaching undergraduate and graduate level courses on algorithms, machine learning, artificial intelligence, data science, and programming languages,
but I'm also able to teach any course in the undergraduate curriculum.
I'm committed to making my classrooms an inclusive environment where all students can succeed.

\noindent
One of my goals as a professor is to get students more involved with open source software.
I designed some of the first courses to teach students how to contribute to open source software,
and the resulting curricula earned an award from SIGCSE's graduate student research competition.
Through these courses and other mentoring, 
I've helped students contribute to and start their own open source projects with collaborators from around the world.
I hope at Cal State LA to offer a course on open source software development,
to integrate open source more closely with the students' other courses,
and to continue to pioneer new ways to involve students in open source software.

\noindent
Thank you for your consideration.
If you have any questions,
please do not hesitate to ask.

\noindent
Regards,

\vspace{-0.10in}
\noindent
Mike Izbicki

%\school{?}{ Christopher T. Ryu: machine learning; Paul Salvador Inventado: data mining for education; }
%
%\school{cpp}{Hao Ji: machine learning and hpc; Amar Raheja: image analysis; Daisy Tang: machine learning for robots; Lan Yang: big data; }
%
%\school{csusb}{Haiyan Qiao: machine learning applied to bioinformatics and games; George M. Georgiou: neural networks with complex numbers;  Qingquan Sun: Compressive Sensing and Machine Learning; Yan Zhang: data mining, distributed computing; }
%
%\school{HMC}{Ben Wiedermann: programming languages; Christopher A. Stone: type theory; George D. Montañez: why machine learning works (hired in 2017); Julie Medero: NLP}
%
%\school{CMC}{Dr. Jeho Park is a co-founder and the Director of Data Analysis for SoDAVi (Social Data Analysis and Visualization), a non-profit organization. He was also elected President (2019 term) of the Korean-American Computer Scientists and Engineers Association. His research and career interests are in high performance computing, data science, AI/Machine Learning, and computer science and mathematics education.}
%
%\school{SDSU}{Dr. Tao Xie, Dr. Mary Thomas: high performance and parallel computing; Dr. Marko Vuskovic: machine learning for robots; Dr. Faramarz Valafar: machine learning for bioinformatics; Dr. Marie Roch: machine learning for mapping marine biology}


\end{document}
